The Impact of Tax Policy Evolution on Economic Development and Income Inequality

### 2024-02-20 paper/paper.qmd
Update paper
Mention R and packages

This paper reproduces, replicates, and expands on these findings. It examines the implications of tax policy evolution on economic development and income inequality, which raises the research question: "How does the transition from indirect to direct taxation, alongside the dynamics of the informal sector, influence tax equity and economic development in low- and middle-income countries, and what are the implications for designing effective and equitable tax policies?"

@@

The original paper, "Tax Equity in Low- and Middle-Income Countries," utilized for replication, was published in the American Economic Association journal in 2024 [@article]. It explores the role of taxation in mitigating income inequality within countries with lower and middle incomes [@article]. This paper seeks to build upon the findings of the original paper, using the same datasets that were last retrieved on February 10th, 2024.

>>>>

This paper reproduces, replicates, and expands on these findings, using the R programming language [@citeR] and the 'tidyverse' [@citeTidyverse] packages. Within the 'tidyverse' package [@citeTidyverse], we used 'readr' [@citeReadr], 'dplyr' [@citeDplyr], 'tidyr' [@citeTidyr], and 'ggplot2' [@citeGgplot2]. It examines the implications of tax policy evolution on economic development and income inequality, which raises the research question: "How does the transition from indirect to direct taxation, alongside the dynamics of the informal sector, influence tax equity and economic development in low- and middle-income countries, and what are the implications for designing effective and equitable tax policies?"

@@

The original paper, "Tax Equity in Low- and Middle-Income Countries," utilized for replication, was published in the American Economic Association journal in 2024 [@article]. Its replication package is from the openICPSR Portal [@openicpsr]. It explores the role of taxation in mitigating income inequality within countries with lower and middle incomes [@article]. This paper seeks to build upon the findings of the original paper, using the same datasets that were last retrieved on February 10th, 2024.
